Draft2

### 2022-04-19 Draft2.Rmd
the graphs are printed for 07. need to see how to combine them together

#SCRATCH WORK ABOVE

@@

#Graph selected countries 
#Is there a way to color by low and high?
combo_07 %>% 
  ggplot(aes(x = country, y = average_death_07_low)) + 
  geom_point()
```

>>>>

```{r}
#SCRATCH WORK ABOVE

@@

#Graph selected countries 
#Is there a way to color by low and high and combine the two graphs below?
combo_07 %>% 
  ggplot(aes(x = country, y = average_death_07_low)) + 
  geom_point()

combo_07 %>% 
  ggplot(aes(x = country, y = average_death_07_high)) + 
  geom_point()
```
